TGI Spinal Analysis Code

### 2022-12-05 analysis/tgi-spinal_analysis.Rmd
small edits

# Loading data
```{r}
# paths
datPath <- '/Users/au706616/Documents/Experiments/SPINALTGI/Raw/'
anaPath <- '/Users/au706616/Documents/Experiments/SPINALTGI/Analysis/'

>>>>

# Loading data
```{r paths, echo = FALSE}
# paths
datPath <- '/Users/au706616/Documents/Experiments/SPINALTGI/Raw/'
anaPath <- '/Users/au706616/Documents/Experiments/SPINALTGI/Analysis/'
